---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# websearchr

The goal of websearchr is to provide a convenient way of accessing domains and searching popular websites directly from the R console. When working on small screens in particular, switching from the R console to the browser window, opening a new tab, navigating to the desired website and finally searching for the search terms requires around 3-6 clicks. As one is working mainly in the R console, it is more convenient to start typing the search terms right away, without having to go through the process mentioned above. For example, `stackoverflow("my r problem")` will open the stackoverflow search for "my r problem" in a new browser tab automatically.

Currently supported websites:

* Bing
* Crossref
* Duckduckgo
* GitHub
* Google
* Google Scholar
* Rdocumentation.org
* rdrr.io
* Stackoverflow
* Twitter
* Wikipedia

Any other website can be accessed with `open(my-website.com)`. 

Bonus: obtain the number of Google hits for a combination of search terms with `google.hits("search terms")`.


## Installation

You can install websearchr from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fschaff/websearchr")
```

Please report issues or requests for additional functionality to https://github.com/fschaff/websearchr/issues

## Example

```{r example}
library(websearchr)

## Try:
open(r-project.org)
google("my search terms")
stackoverflow("my r problem")
```
