---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# websearchr

The goal of **websearchr** is to provide a convenient way of accessing domains and searching popular websites directly from the R console. When working on small screens in particular, switching from the R console to the browser window, opening a new tab, navigating to the desired website and finally searching for the search terms requires around 3-6 clicks. As one is working mainly in the R console, it is more convenient to start typing the search terms right away, without having to go through the process mentioned above. For example, `stackoverflow("my r problem")` will open the stackoverflow search for "my r problem" in a new browser tab automatically.

Currently supported websites:

* Bing
* Crossref
* Duckduckgo
* GitHub
* Google
* Google Scholar
* Qwant
* r-bloggers.com
* Rdocumentation.org
* rdrr.io
* Reddit
* Stackoverflow
* Twitter
* Wikipedia
* Wolfram Alpha

Any other domain can be accessed with `web(my-website.com)`. 


#### Browser

To use a browser other than the default on your computer use `options(browser = "path to browser")`. For example, on Mac OS X `options(browser = "/usr/bin/open -a '/Applications/Safari.app'")` or Windows `options(browser = "C:\\Program Files (x86)\\Internet Explorer\\iexplore.exe")`. To check which browser is set as the default use `getOption("browser")`.


## Installation

[![CRAN Version](https://www.r-pkg.org/badges/version/websearchr)](https://cran.r-project.org/package=websearchr) 
![Downloads](https://cranlogs.r-pkg.org/badges/websearchr)
[![Build Status](https://travis-ci.org/fschaff/websearchr.svg?branch=master)](https://travis-ci.org/fschaff/websearchr)

You can install websearchr from CRAN with:
```{r cran-installation, eval = FALSE}
install.packages("websearchr")
```

Or install the development version from GitHub:
```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("fschaff/websearchr")
```

Please report issues or requests for additional functionality to https://github.com/fschaff/websearchr/issues.

## Example

```{r example}
library(websearchr)

# Try:

web("r-project.org")

google("my search terms")

stackoverflow("my r problem")
```
